Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-11 Manuscript.qmd
Update results for authenticity scores' prediction

### Respondent Characteristics
167 respondents were eligible for the data analysis after data cleaning. Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old. The average age of the sample was `r round(mean(queer.hypo$age), 2)` years old (*SD* = `r round(sd_age, 2)`). This wide age range ensured the study captured perspectives from individuals across different generations. Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective. Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender. Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender. The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2). The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native. This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersecting identities.

@@

>>>>

### Respondent Characteristics
167 respondents were eligible for the data analysis after data cleaning. Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old. The average age of the sample was `r round(mean(queer.hypo$age), 1)` years old (*SD* = `r round(sd_age, 1)`). This wide age range ensured the study captured perspectives from individuals across different generations. Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective. Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender. Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender. The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2). The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native. This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersecting identities.

@@

## Predictors of Queer Media Characters’ Psychological Impacts

### Queer Media Consumption Habits

Data visualization of bubble plots revealed that queer media exposure frequency and engagement may predict queer media characters’ psychological impacts on LGBTQ+ individuals. The bubble plot for queer media exposure and discussion frequency indicated that developed countries have more participants who engaged less with queer media characters, which may contribute to lower impact scores (Figure 7). Though bubbles for developing countries were smaller, it was the result of a much smaller sample size (N = 22) for developing countries' residents than for developed countries' residents (N = 145). The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (Figure 8), which may contribute to higher community belong scores and the overall psychological impact scores.

```{r}
#| label: fig-plot-country-freq
#| fig-cap: Country Differences in Queer Media Exposure Frequency and Engagement
#| fig-width: 15
#| fig-height: 5

create_country_bubble_plot <- function(queer.hypo, y_var, title) {
  ggplot(queer.hypo, aes(x = development_status, y = !!sym(y_var))) +
    geom_count(aes(size = ..n..), alpha = 0.6, color = "blue") +  
    labs(title = title,
         x = "Development Status",
         y = y_var) +
    scale_size_area(max_size = 15, name = "Count") +  
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.title.x = element_text(hjust = 0.5),  
      axis.text.x = element_text(hjust = 0.5),  
      legend.position = "bottom",  
      legend.title = element_text(size = 8),
      legend.text = element_text(size = 7),  
      legend.key.size = unit(0.5, "cm"),
      plot.margin = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")  # Reduce margin
    ) +
    guides(size = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5))}  # Adjust legend layout

country_freq_bubbleplot <- create_country_bubble_plot(queer.hypo, "frequency", "Frequency")
country_seek_bubbleplot <- create_country_bubble_plot(queer.hypo, "actively_seek_out", "Actively Seek Out Queer Representations")
country_discussion_bubbleplot <- create_country_bubble_plot(queer.hypo, "discussion", "Discussion Engagement of Queer Media Representations")

combined_country_bubble_plot <- grid.arrange(country_freq_bubbleplot, country_seek_bubbleplot, country_discussion_bubbleplot, ncol = 3)

```{r}
#| label: fig-plot-gender-freq
#| fig-cap: Gender Differences in Queer Media Exposure Frequency and Engagement
#| fig-width: 15
#| fig-height: 5

create_gender_identity_bubble_plot <- function(queer.hypo, y_var, title) {
  ggplot(queer.hypo, aes(x = gender_identity_dual, y = !!sym(y_var))) +
    geom_count(aes(size = ..n..), alpha = 0.6, color = "blue") +  
    labs(title = title,
         x = "Gender Identity",
         y = y_var) +
    scale_size_area(max_size = 15, name = "Count") +  
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.title.x = element_text(hjust = 0.5),  
      axis.text.x = element_text(hjust = 0.5),  
      legend.position = "bottom",  
      legend.title = element_text(size = 8),  
      legend.text = element_text(size = 7),  
      legend.key.size = unit(0.5, "cm"),
      plot.margin = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")  
    ) +
    guides(size = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5))}

gender_identity_freq_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "frequency", "Frequency")
gender_identity_seek_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "actively_seek_out", "Actively Seek Out Queer Representations")
gender_identity_discussion_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "discussion", "Discussion Engagement of Queer Media Representations")

combined_gender_identity_bubble_plot <- grid.arrange(gender_identity_freq_bubbleplot, gender_identity_seek_bubbleplot, gender_identity_discussion_bubbleplot, ncol = 3)

### Perceived Queer Character Authenticity

```{r}
#| label: Linear regression for authenticity rating predicting psychological well-being scores
#| include: false

authenticity.effect <- lm(psychological_wellbeing_score ~ authenticity_rating, data = queer.hypo)
summary(authenticity.effect)

summary_authenticity <- summary(authenticity.effect)

f_statistic_auth <- summary_authenticity$fstatistic[1]
df1_auth <- summary_authenticity$fstatistic[2]
df2_auth <- summary_authenticity$fstatistic[3]
r_squared_auth <- summary_authenticity$r.squared[1]
p_value_auth <- pf(f_statistic_auth, df1_auth, df2_auth, lower.tail = FALSE)

A linear regression was conducted to examine the relationship between authenticity rating and psychological wellbeing scores. The results indicated a significant effect of authenticity rating on psychological wellbeing (*F*(`r df1_auth`, `r df2_auth`) = `r round(f_statistic_auth, 2)`, *p* `r if(p_value_auth < .001) "< .001" else paste("=", round(p_value_auth, 3))`). The $R^2$ was `r round(r_squared_auth,3)`, indicating that the perceived queer character authenticity explained `r round(r_squared_auth * 100, 1)`% of the variance in psychological wellbeing scores. This result suggests that the more authentic LGBTQ+ individuals perceive queer media characters, the more positive psychological impacts they may experience.

Figure 9 illustrates that the authencity rating positively predicts psychological well-being scores for both developed and developing countries' residents. The regression line for developing countries' residents is steeper than that for developed countries' residents, indicating that the authenticity rating has a stronger effect on psychological well-being scores for developing countries' residents.

Figure 10 indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities. The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men. Nevertheless, given the fact that men have lower psychological impacts scores, the authenticity rating may not be the only factor influencing psychological impact scores.

```{r}
#| label: fig-plot-auth-psych-impact-country
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Country
#| message: false
#| fig-width: 10
#| fig-height: 5
auth.psych.dev <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
  geom_point(aes(colour = development_status, shape = development_status)) +                                
  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
  labs(title = "Authenticity Rating Predicting Psychological Effects by Development Status") + 
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  scale_x_continuous(
    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
  ) +
  stat_smooth(method = "lm", aes(fill = development_status, colour = development_status)) +    
  scale_colour_manual(name = "Development Status", values = c("#FFC125", "#36648B")) +
  scale_fill_manual(name = "Development Status",values = c("#FFC125", "#36648B")) +
  scale_shape_discrete(name = "Development Status") +
  theme.clean()

print(auth.psych.dev)

```{r}
#| label: fig-plot-auth-psych-impact-gender
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Gender Identity
#| message: false
#| fig-width: 10
#| fig-height: 5.5

auth.psych.gender <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
  geom_point(aes(colour = gender_identity_dual, shape = gender_identity_dual)) +                                
  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
  labs(title = "Authenticity Rating Predicting Psychological Effects by Gender Identity") + 
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  scale_x_continuous(
    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
  ) +
  stat_smooth(method = "lm", aes(fill = gender_identity_dual, colour = gender_identity_dual)) +    
  scale_colour_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
  scale_fill_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
  scale_shape_discrete(name = "Gender Identity") +
  theme.clean()

print(auth.psych.gender)

Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low scores for both ratings. This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of queer media characters.

Figure 12 shows that the authenticity rating positively predicts psychological well-being scores for all racial identities. The regression line for black, asian, and indian respondents is slightly steeper, indicating that the authenticity rating has a stronger effect on psychological well-being scores for these respondents. This result suggests that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character authenticity than white respondents.

```{r}
#| label: fig-plot-auth-psych-impact-orientation
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Sexual Orientation
#| message: false
#| fig-width: 11
#| fig-height: 5.5

auth.psych.orientation <- ggplot(queer.hypo_filtered, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
  geom_point(aes(colour = sexual_orientation, shape = sexual_orientation)) +                                
  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Sexual Orientation") + 
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  scale_x_continuous(
    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
  ) +
  stat_smooth(method = "lm", aes(fill = sexual_orientation, colour = sexual_orientation)) +    
  scale_colour_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
  scale_fill_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
  scale_shape_discrete(name = "Sexual Orientation") +
  facet_wrap(~sexual_orientation) +
  theme.clean()

print(auth.psych.orientation)

```{r}
#| label: fig-plot-auth-psych-impact-race
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Racial Identity
#| message: false
#| fig-width: 11.5
#| fig-height: 5.5

auth.psych.race <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
  geom_point(aes(colour = race_category, shape = race_category)) +                                
  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Racial Identity") + 
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  scale_x_continuous(
    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
  ) +
  stat_smooth(method = "lm", aes(fill = race_category, colour = race_category)) +    
  scale_colour_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
  scale_fill_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
  scale_shape_discrete(name = "Racial Identity") +
  theme.clean()

print(auth.psych.race)
